---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LostFound

<!-- badges: start -->
[![R build status](https://github.com/aboskovic21/LostFound/workflows/R-CMD-check/badge.svg)](https://github.com/aboskovic21/LostFound/actions)
<!-- badges: end -->

The goal of LostFound is to provide a useful data set in R.

This data set comes from DataIsPlural available as a spreadsheet [here.](https://docs.google.com/spreadsheets/d/1wZhPLMCHKJvwOkP4juclhjFgqIY8fQFMemwKL2c64vk/edit#gid=0) It is from 12/30/2015, with the headline "Things lost (and not yet found) on the New York subway." This lists an a GitHub repository with the dataset as well.

Fivethirtyeight has an interesting article with some interesting findings about this dataset [here.](https://fivethirtyeight.com/features/mta-new-york-lost-and-found-subway-most-common/)

## Installation

You can install the released version of LostFound from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
remotes::install_github("aboskovic21/LostFound")
```
 
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(LostFound)
summary(LostFound)
```
